Convolutional Neural Networks on Graphs\\ with Fast Localized Spectral Filtering

### 2016-10-31 nips2016/nips2016.tex
makefile: image creation
arxiv v2 (2016-10-31)

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

@@

In this work, we are interested in generalizing convolutional neural networks
(CNNs) from low-dimensional regular grids, where image, video and speech are
represented, to high-dimensional irregular domains, such as social networks,
brain connectomes or words’ embedding, represented by graphs.
We present a formulation of CNNs in the context of spectral graph theory, which
provides the necessary mathematical background and efficient numerical schemes
to design fast localized convolutional filters on graphs. Importantly, the
proposed technique offers the same linear computational complexity and constant
learning complexity as classical CNNs, while being universal to any graph
structure. Experiments on MNIST and 20NEWS demonstrate the ability of this
novel deep learning system to learn local, stationary, and compositional
features on graphs.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{images/coarsening_crop}
\caption{\textbf{Example of Graph Coarsening and Pooling.} Let us carry out a max pooling of size 4 (or two poolings of size 2) on a signal $x \in
\R^8$ living on $\G_0$, the finest graph given as input. Note that it originally
possesses $n_0 = |\V_0| = 8$ vertices, arbitrarily ordered. For a pooling of
size 4, two coarsenings of size 2 are needed: Graclus first gives $\G_1$ of size
$n_1 = |\V_1| = 5$, then $\G_2$ of size $n_2 = |\V_2| = 3$, the coarsest graph.
Sizes are thus set to $n_2 = 3$, $n_1 = 6$, $n_0 = 12$ and fake nodes (in blue)
are added to $\V_1$ (1 node) and $\V_0$ (4 nodes) to pair with the singeltons
(in orange), such that each node has exactly two children.  Nodes in $\V_2$ are
then arbitrarily ordered and nodes in $\V_1$ and $\V_0$ are ordered
consequently.  At that point the arrangement of vertices in $\V_0$ permits a
regular 1D pooling on $x \in \R^{12}$ such that $z = [\max(x_0,x_1),
\max(x_4,x_5,x_6), \max(x_8,x_9,x_{10})] \in \R^3$, where the signal components
$x_2,x_3,x_7,x_{11}$ are set to a neutral value.}
\label{fig:pooling}
\end{figure}

@@

\begin{table*}[t]
\begin{minipage}[b]{0.42\linewidth}
	\centering
	\begin{tabular}[b]{lc}
		\toprule
		Model & Accuracy \\
		\midrule
		Linear SVM & 65.90 \\
		Multinomial Naive Bayes & 68.51 \\
		%Multinomial logistic regression (softmax) & 66.28 \\
		Softmax & 66.28 \\
		\addlinespace
		FC2500 & 64.64 \\
		FC2500-FC500 & 65.76 \\
		\addlinespace
		GC32 & 68.26 \\
		%GC32-FC500 & \todo{?} \\
		\bottomrule
	\end{tabular}
	\caption{Accuracies of the proposed graph CNN and other
	methods on 20NEWS.} 
	\label{tab:20news}
\end{minipage}
\hfill
\begin{minipage}[b]{0.55\linewidth}
	\centering
	\includegraphics[width=\textwidth]{images/runtime_crop}
	\captionof{figure}{Time to process a mini-batch of $S=100$ 20NEWS documents
	w.r.t. the number of words $n$.}
	\label{fig:runtime}
\end{minipage}
\end{table*}

>>>>

\documentclass{article}
\pdfoutput=1  % for arXiv to use pdflatex

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
\PassOptionsToPackage{numbers}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

@@

In this work, we are interested in generalizing convolutional neural networks
(CNNs) from low-dimensional regular grids, where image, video and speech are
represented, to high-dimensional irregular domains, such as social networks,
brain connectomes or words' embedding, represented by graphs.
We present a formulation of CNNs in the context of spectral graph theory, which
provides the necessary mathematical background and efficient numerical schemes
to design fast localized convolutional filters on graphs. Importantly, the
proposed technique offers the same linear computational complexity and constant
learning complexity as classical CNNs, while being universal to any graph
structure. Experiments on MNIST and 20NEWS demonstrate the ability of this
novel deep learning system to learn local, stationary, and compositional
features on graphs.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{images/coarsening}
\caption{\textbf{Example of Graph Coarsening and Pooling.} Let us carry out a max pooling of size 4 (or two poolings of size 2) on a signal $x \in
\R^8$ living on $\G_0$, the finest graph given as input. Note that it originally
possesses $n_0 = |\V_0| = 8$ vertices, arbitrarily ordered. For a pooling of
size 4, two coarsenings of size 2 are needed: Graclus first gives $\G_1$ of size
$n_1 = |\V_1| = 5$, then $\G_2$ of size $n_2 = |\V_2| = 3$, the coarsest graph.
Sizes are thus set to $n_2 = 3$, $n_1 = 6$, $n_0 = 12$ and fake nodes (in blue)
are added to $\V_1$ (1 node) and $\V_0$ (4 nodes) to pair with the singeltons
(in orange), such that each node has exactly two children.  Nodes in $\V_2$ are
then arbitrarily ordered and nodes in $\V_1$ and $\V_0$ are ordered
consequently.  At that point the arrangement of vertices in $\V_0$ permits a
regular 1D pooling on $x \in \R^{12}$ such that $z = [\max(x_0,x_1),
\max(x_4,x_5,x_6), \max(x_8,x_9,x_{10})] \in \R^3$, where the signal components
$x_2,x_3,x_7,x_{11}$ are set to a neutral value.}
\label{fig:pooling}
\end{figure}

@@

\begin{table*}[t]
\begin{minipage}[b]{0.42\linewidth}
	\centering
	\begin{tabular}[b]{lc}
		\toprule
		Model & Accuracy \\
		\midrule
		Linear SVM & 65.90 \\
		Multinomial Naive Bayes & 68.51 \\
		%Multinomial logistic regression (softmax) & 66.28 \\
		Softmax & 66.28 \\
		\addlinespace
		FC2500 & 64.64 \\
		FC2500-FC500 & 65.76 \\
		\addlinespace
		GC32 & 68.26 \\
		%GC32-FC500 & \todo{?} \\
		\bottomrule
	\end{tabular}
	\caption{Accuracies of the proposed graph CNN and other
	methods on 20NEWS.} 
	\label{tab:20news}
\end{minipage}
\hfill
\begin{minipage}[b]{0.55\linewidth}
	\centering
	\includegraphics[width=\textwidth]{images/runtime}
	\captionof{figure}{Time to process a mini-batch of $S=100$ 20NEWS documents
	w.r.t. the number of words $n$.}
	\label{fig:runtime}
\end{minipage}
\end{table*}
